Machines are Among Us

### 2020-12-02 paper/main.tex
added some information in results and approach

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
The two opposing models were trained
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant tcooperative models ratrher than against the adversarial model.

Furthermore, the immense number of combinations of hyperparameters
and input and outputs sizes, along with no precedent for recommended values,
lead us to generalize our model significantly. Although this may seem like an ability for
customizability, it severely reduces reproducability over small changes.

@@

A typical training session started with the first two initial epochs,
as discussed previously

@@

Due to resource constraints, we were not able to get as much 
data as we had hoped for.
This lead to a consistency issue, where the same variable combination would yield
different results because of certain randomness within training the models.
\subsection{Oscillating Scores}
The hopeful goal was to find the set of variables that lead to not only a convergence,
but an almost "tug-of-war" battle when one model trains against the other and vice versa.
This is graphically shown via an oscillating crew score around the 
eventual convergence crew score. This would mean that the two models
are successfunlly balanced and able to improve their strategy with training time against
the opposition.

In an attempt to find a training session mathcing this quality

% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
Unfortunately, we could not 
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\appendix
\section{Reproducibility}
\section{Framework}
\end{document}

>>>>

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Similar to GANs, we decided the best approach to train the two adversarial models was to
use alternating training to help find eventual convergence and juggle two different
optimizations.

\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant cooperative models ratrher than against the adversarial model.

Furthermore, the immense number of combinations of hyperparameters
and input and outputs sizes, along with no precedent for recommended values,
lead us to generalize our model significantly. Although this offers the extended ability for
customizability and exploration, it severely reduces reproducability over small changes.

@@

A typical training session started with the first two alternating epochs,
which were considered as the "initialization" of the two models. Training the imposters
first gave them time to learn to note vote for each other. Then, the crew
had learned the same thing on the next epoch. After this initial training,
then the models started to significantly train against each other.

@@

Due to resource constraints, we were not able to get as much 
data as we had hoped for.
This lead to a consistency issue, where the same variable combination would yield
different results because of certain randomness within training the models.

\subsection{Oscillating Scores}
The hopeful goal was to find the set of variables that lead to not only a convergence,
but an almost "tug-of-war" battle when one model trains against the other and vice versa.
This is graphically shown via an oscillating crew score around the 
eventual convergence crew score. This would mean that the two models
are successfunlly balanced and able to improve their strategy with training time against
the opposition.

\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
Unfortunately, we could not fully interpret the communication vectors due to the
disconnect between representation of information. However, we found an 
interesting result when the players were given no identifying information (e.g. 
there were no sabotages whatsoever in the percpetion stage), the crew could still
win the situation. At first glance, this seems almost impossible because the crew would
be unable to identify the imposters via the necessary events. Further thought lead us
to make an estimated conclusion that the crew model was actual creating a hidden tag or key
to identify themselves within the commmunication stage, therefore identifying the imposters 
immediately. The imposters would then have to train to figure out this key or
become helpless. This situation resembles almost a cryptographic adversarial problem,
unlocking more future directions this work could potentially travel.
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

@@

Finally, similar work in adversarial networks could potentially give rise to
more techniques utilizing them. Generative adversarial networks are at the forefront of adversarial techniques, but possibly
large multi-agent adervasarial communication networks could give heed to more good results.
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
\appendix
\section{Reproducibility}
Reproducibility might yield different results due to the random creation of data and
weight setting.

The parameters used for Figure 2, the grid search, are:

\begin{tabular}{ |c|c| } 
\hline 
"B" & 64 \\
\hline
"N" & 16 \\
\hline
"H"& 256 \\
\hline
"M"& 12 \\
\hline
"ROUNDS"& 0 \\
\hline
"P"& 10 \\
\hline
"I"& 2 \\
\hline
"EPOCHS"& 6 \\
\hline
"EPOCH LENGTH"& 1024 \\
\hline
"VIEW CHANCE"& 0.5 \\
\hline
"SABOTAGE CHANCE"& 0.5 \\
\hline
"TRAIN CREW FIRST"& false \\
\hline
"TRAIN SINGLE CREWMATE"& true \\
\hline
"CONST CREW COPY FREQ"& 32 \\
\hline
"TRAIN SINGLE IMPOSTER"& true \\
\hline
"CONST IMPOSTER COPY FREQ"& 32 \\
\hline
"PRINT FREQ"& 64 \\
\hline
"SAVE EPOCH FREQ"& 2 \\
\hline
\end{tabular}
\section{Framework}
The framework we used for our project
was PyTorch, and build the model based off of their implementation
of an LSTM and MLP layers. 
\end{document}
